PyPy – status and next goals

### 2008-04-09 talk/rupy2008/talk.tex
mention anto, more advantages
Typo
drop few XXXs

\begin{frame}
  \frametitle{What is PyPy?}
  \begin{itemize}
  \item
    A flexible toolkit for writing interpreters
    \begin{itemize}
      \item
        giving you lots of ameninities
      \item
        translation to lots of environments
      \item
        a mostly good GC
      \item
        libraries
      \item
        a JIT
    \end{itemize}
  \pause
  \item
    the biggest implemented interpreter is a full Python interpreter
    \begin{itemize}
      \item
        implementing Python 2.4 semantics fully
      \item
        extra features
      \item
        lazy evaluation
      \item
        stackless
      \item
        various introspection enhancements
    \end{itemize}
  \item
    Open Source project (MIT licenced)
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{CTypes}
  \begin{itemize}
  \item CTypes is a libffi wrapper for CPython
  \item implemented in C
  \item can be used to wrap C libraries rather effortlessly
  \item no need to write C code to interface with libraries

@@

\begin{frame}
  \frametitle{Garbage Collection}
  \begin{itemize}
  \item RPython itself is garbage collected
  \item when translating to C, a GC is woven into the program
  \item GCs are completely written in Python
  \item similar to the MMTK toolkit of Jikes RVM
  \item two fast GCs: semispace, generational
  \item lots of care to get the semantics right:
    \begin{itemize}
    \item finalizers, weakrefs
    \item id function
    \item identity hashes
    \end{itemize}
  \item performance pretty good
  \item memory-bound benchmarks faster than CPython
  \item demo (id(x))
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Advantages of JIT Generation}
  Writing a JIT generator is hard, but:
  \begin{itemize}
  \item You only need to do it once
  \item the effort of writing a JIT generator is independent of the size of the language
  \item can keep up with language evolution
  \item XXX
  \item it's fun too
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{What is PyPy?}
  \begin{itemize}
  \item
    A flexible toolkit for writing interpreters
    \begin{itemize}
      \item
        giving you lots of ameninities
        XXX don't use such words IMO, try to be more understandable
        XXX audience is mostly students
      \item
        translation to lots of environments
      \item
        a mostly good GC
      \item
        libraries
      \item
        a JIT
    \end{itemize}
  \pause
  \item
    the biggest implemented interpreter is a full Python interpreter
    \begin{itemize}
      \item
        implementing Python 2.4 semantics fully
      \item
        extra features
      \item
        lazy evaluation
        XXX I don't like advertising features that don't work
      \item
        stackless
      \item
        various introspection enhancements
    \end{itemize}
  \item
    Open Source project (MIT licenced)
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{CTypes}
  \begin{itemize}
  \item CTypes is a libffi wrapper for CPython
  \item implemented in C
  \item can be used to wrap C libraries rather effortlessly
  \item no need to write C code to interface with libraries
        XXX ctypes demo maybe...

@@

\begin{frame}
  \frametitle{Garbage Collection}
  \begin{itemize}
  \item RPython itself is garbage collected
        XXX this is the first time you mention RPython, that's
        XXX either too late, or not mention it at all
  \item when translating to C, a GC is woven into the program
        XXX another hard word
  \item GCs are completely written in Python (XXX RPython)
  \item similar to the MMTK toolkit of Jikes RVM
  \item two fast GCs: semispace, generational
  \item lots of care to get the semantics right:
    \begin{itemize}
    \item finalizers, weakrefs
    \item id function
    \item identity hashes
    \end{itemize}
  \item performance pretty good
  \item memory-bound benchmarks faster than CPython
  \item demo (id(x))
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Advantages of JIT Generation}
  Writing a JIT generator is hard, but:
  \begin{itemize}
  \item You only need to do it once
  \item the effort of writing a JIT generator is independent of the size of the language
  \item can keep up with language evolution
  \item retargetting the JIT is possible (e.g. to .NET, as Antonio Cuni is doing right now)
  \item make the JIT behave radically differently is much easier with a generator
  \item it's fun too
  \end{itemize}
\end{frame}
